### 2024-08-01 Paper/paper2.tex
Updates from Overleaf

    \begin{figure}[ht!]
     \caption{Effect of Clinical Experience on Readmission Rates, Binned Treatment}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{$0 < \rho \leq .25$}
         \includegraphics[width=\textwidth]{Objects/cont_onefourthread_md_nomd_synth_graph.pdf}
         \label{fig:onefourth_read_synth_clinical}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{$.25 < \rho \leq .5$}
         \includegraphics[width=\textwidth]{Objects/cont_onehalfread_md_nomd_synth_graph.pdf}
         \label{fig:onehalf_read_synth_clinical}
     \end{subfigure}
        \label{fig:cont_clinicalsynthdid}
    \end{figure}

@@

    \begin{figure}[ht!]
     \caption{Effect of Clinical Experience on Mortality Rates, Binned Treatment}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{$0 < \rho \leq .25$}
         \includegraphics[width=\textwidth]{Objects/cont_onefourthmort_md_nomd_synth_graph.pdf}
         \label{fig:onefourth_mort_synth_clinical}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{$.25 < \rho \leq .5$}
         \includegraphics[width=\textwidth]{Objects/cont_onehalfmort_md_nomd_synth_graph.pdf}
         \label{fig:onehalf_mort_synth_clinical}
     \end{subfigure}
        \label{fig:cont_clinicalsynthdid_mort}
    \end{figure}

@@

    While most doctors still take a hippocratic oath to care for patients with integrity and compassion, doctors with training in certain specialties may be more equipped to improve care for patients with the specific conditions relevant in this context. Specifically, a pulmonologist typically treats pneumonia, and a cardiologist typically treats heart failure and heart attack patients, which are the three conditions considered in the HRRP penalties. Both of these specialties are under the umbrella of internal medicine. My physician specialty information does not get more granular than internal medicine as a specialty. Thus, I estimate the difference in response between

>>>>

    \begin{figure}[ht!]
     \caption{Effect of Clinical Training on Readmission Rates, Binned Treatment}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{$0 < \rho \leq .25$}
         \includegraphics[width=\textwidth]{Objects/cont_onefourthread_md_nomd_synth_graph.pdf}
         \label{fig:onefourth_read_synth_clinical}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{$.25 < \rho \leq .5$}
         \includegraphics[width=\textwidth]{Objects/cont_onehalfread_md_nomd_synth_graph.pdf}
         \label{fig:onehalf_read_synth_clinical}
     \end{subfigure}
        \label{fig:cont_clinicalsynthdid}
    \end{figure}

@@

    \begin{figure}[ht!]
     \caption{Effect of Clinical Training on Mortality Rates, Binned Treatment}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{$0 < \rho \leq .25$}
         \includegraphics[width=\textwidth]{Objects/cont_onefourthmort_md_nomd_synth_graph.pdf}
         \label{fig:onefourth_mort_synth_clinical}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{$.25 < \rho \leq .5$}
         \includegraphics[width=\textwidth]{Objects/cont_onehalfmort_md_nomd_synth_graph.pdf}
         \label{fig:onehalf_mort_synth_clinical}
     \end{subfigure}
        \label{fig:cont_clinicalsynthdid_mort}
    \end{figure}

@@

    While most doctors still take a hippocratic oath to provide care with integrity and compassion, doctors with training in certain specialties may be more equipped to improve care for patients with the particular conditions relevant in this context. Specifically, a pulmonologist typically treats pneumonia, and a cardiologist typically treats heart failure and heart attack patients, which are the three conditions considered in the HRRP penalties. Both of these specialties are under the umbrella of internal medicine. The physician specialty information in my data does not get more granular than internal medicine as a specialty. Thus, I estimate the difference in response between internal medicine physicians and other specialty physicians.

    \begin{figure}[ht!]
     \caption{Effect of Internal Medicine Training on Quality}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{Readmission Rates}
         \includegraphics[width=\textwidth]{Objects/read_specialty_synth_graph.pdf}
         \label{fig:read_spec}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{Mortality Rates}
         \includegraphics[width=\textwidth]{Objects/mort_specialty_synth_graph.pdf}
         \label{fig:mort_spec}
     \end{subfigure}
        \label{fig:specialty}
    \end{figure}
